The reference model approach in feature selection problems \vspace{.1in}

### 2019-07-17 paper/ref_approach.tex
more edits to section 3

In our examples, we retrieve the normal means problem from the sample correlations between the target and the covariates using the Fisher $z$-transformation \citep{hawkins1989using}. Suppose we have a continuous target random variable $Y$, a set of $p$ continuous covariates $\{X_{j}\}_{j=1}^{p}$, and let us denote $\rho_{j}=Cor(Y,X_{j})$. Further, suppose we have observed $n$ statistical units and define $r_{j}$ the sample correlation between the observations of the target variables $\{y_{i}\}_{i=1}^{n}$ and the $j$-th covariate $\{x_{ij}\}_{i=1}^{n}$. Finally, we refer to the Fisher $z$-transformation function $\text{tanh}^{-1}(\cdot)$ as $T_{F}(\cdot)$. Assuming each pair $(Y,X_{j})$ to be bivariate normally distributed, the corresponding transformed correlations are approximately normally distributed as well with known variance:
\
\begin{equation} \label{eq:fisher_transformation}
T_{F}(r_{j})\overset{ind}{\sim} N(T_{F}(\rho_{j}),\frac{1}{n-3}) \quad j=1,..,p
\end{equation}
Therefore, rescaling the quantities $T_{F}(r_{j})$ by $\sqrt{n-3}$ and referring to the results as variables $z_{j}$, we again find the formulation \eqref{eq:normal_means_problem} of the normal means problem, this time with unit variance:
\
\begin{equation} \label{eq:normal_means_problem2}
Z_{j}|\theta_{j}\overset{ind}{\sim}N(\theta_{j},1) \quad j=1,..,p
\end{equation}
Note that in thise cse the quantities of interest $\theta_{j}$ are equal to $\sqrt{n-3}\,T_{F}(\rho_{j})$. There are different ways to proceed with the selection in the normal means problem. Here, we consider several state-of-the-art approaches from both Bayesian and frequentist statistics (TODO: do we actually consider frequentist approaches here?)

We begin by explaining some Bayesian estimation methods to solving the normal means problem. They all have in common that a Bayesian regression model is fitted using some sparsifying prior on the regression coefficients, for example, as discussed in \cite{paper:dirichlet_laplace}, \cite{bhadra2017horseshoe+} and \cite{johnstone2004needles}. If these priors have continuous support, as is the case for the Dirichlet-Laplace (DL; cite) or horseshoe-like priors (cite), there is no canonical way to complete the selection since the posterior probability of an exactly zero signal is always zero. \cite{paper:dirichlet_laplace} suggest k-means clustering over the posterior samples using the DL prior, whereas \cite{bhadra2017horseshoe+} focus the analysis on the obtained shrinkage and the correct estimation of the sparse signals using the horseshoe+ prior (TODO: is this related to the former sentence?). In our experiments, we include the DL prior and the regularised horseshoe (RHS) prior \citep{paper:rhs}, which we think scales better to higher number of covariates as compared to other horseshoe-like priors. For the Bayesian regression models with these priors, we compare the posterior shrinkage and the correct estimation of the sparse signals with and without using a reference model as a noise filter. For this purpose, we consider the   average SSE (sum of square errors) and the average SESE (sum of expected square errors) as quantities measuring estimation accuracy. They are defined as
\
\begin{align}
\text{SSE}&=\frac{1}{n-3}\sum_{j=1}^{p}(\hat{\theta}_{j} - \theta^{0}_{j})^{2} \label{eq:SSE} \\
\text{SESE}&=\frac{1}{n-3}\sum_{j=1}^{p}\int_{\mathbb{R}}(\theta_{j}-\theta^{0}_{j})^{2}p(\theta_{j}|z_{1},..,z_{p})d\theta_{j} \\
&=\frac{1}{n-3}\sum_{j=1}^{p}\mathbb{E}_{\theta_{j}}[(\theta_{j}-\theta^{0}_{j})^{2}|z_{1},..,z_{p}] \label{eq:SESE}
\end{align}
where $\theta_{j}^{0}=\sqrt{n-3}\,T_{F}(\rho_{j})$ is the true value, $\hat{\theta}_{j}$ is the posterior median of each parameter $\theta_{j}$. We divide the errors by $(n-3)$ to have quantities independent of the number of statistical units. Note that the SESE takes the posterior uncertainty in account and thus also the shrinkage of the posterior distributions, whereas the SSE only measures the bias in the point estimates. Note that actually any kind of point estimate could be used to compute the SSE but here we follow \cite{paper:dirichlet_laplace} and use the posterior median. The results that we show later on in Section \ref{shrinkage-signal} are not sensible to such a choice.

We also take into account the posterior mean for the shrinkage factor ($\kappa_{j}$) for each parameter $\theta_{j}$, which for model \eqref{eq:normal_means_problem2} with a hierarchical shrinkage prior of the type (TODO: please motivate why looking at shrinkage factors is relevant)
\begin{align}
Z_{j}|&\theta_{j}\overset{ind}{\sim}N(\theta_{j},1) \qquad j=1,..,p \\
&\theta_{j}|\tau,\nu_{j}\overset{ind}{\sim}N(0,\nu_{j}^{2}\tau^{2})
\end{align}
is defined as
\begin{equation}
\kappa_{j}=\frac{1}{1+\tau^{2}\nu_{j}^{2}}.
\end{equation}
\
In our case, $\kappa_{j}$ can be computed as
\begin{equation}
\kappa_{j}^{\text{RHS}}=\frac{1}{1+\tau^{2}\lambda_{j}^{2}}, \qquad \kappa_{j}^{\text{DL}}=\frac{1}{1+\psi\phi_{j}^{2}\tau^{2}}
\end{equation}
respectively for the regularised horseshoe and the Dirichlet-Laplace priors. In the left hand-side expression, $\tau$ and $\lambda_{j}$ represent the global and local shrinkage parameters of the regularised horseshoe prior \cite[for further details see][]{paper:rhs}, whereas on the right hand-side, $\psi\phi_{j}^{2}\tau^{2}$ is the variance term of the Dirichlet-Laplace prior of parameter $\theta_{j}$ following the notation of \cite{paper:dirichlet_laplace}.

Within the set of complete selection procedures, we consider three 
Bayesian methods which are described in the following.
\cite{johnstone2004needles} use a spike-and-slab type prior given by a mixture of a delta distribution in zero and a heavy-tailed distribution \cite[see also][]{paper:spike_slab_mitchell}. When the latter is a Laplace distribution, they show an interesting thresholding property of the median estimator and, based on this observation, present a complete selection procedure using their prior. We refer to this method as EB.med. In our experiments, we not only include the EB.med on its own but also in combination with an additional control of the local false discovery rate (loc.fdr) as described in \cite{paper:efron, efron2012large}. Further, we device a simple selection procedure based on posterior credible intervals using the regularised horseshoe prior in which we select covariates whose 90\% credible intervals excludes zero (ci.90). All of these methods provide a complete selection procedure and we compare their performance with and without using a reference model on top of them. As criteria of selection performance, we evaluate the average false discovery rate (i.e., the ratio of the number of non-relevant selected features over the number of selected features) and the average sensitivity (i.e., the ratio of the number of relevant selected features over the total number of relevant features). We also provide a comparison of the stability of the selection by means of a stability measure proposed by \cite{paper:stability}. Table \ref{tab:comparison} summarises the methods used in out numerical experiments.

@@

Here we use simulated data in order to control the difficulty of the selection problem. We rely on the scheme \eqref{eq:simulated_data} using different levels of correlation ($\rho$) and number observation ($n$), precisely $p$ and $k$ are fixed respectively at $1000$ and $100$, whereas $n\in\{50,70,100\}$ and $\rho\in\{0.3,0.5\}$. Lower the correlation level and the number of observations are, more challenging the selection is. As mentioned, this data generation mechanism was already proposed by \cite{paper:projpred}, who also devise a reference model sufficiently good in predictions. It consists in a linear regression using the first five supervised principal components (SPCs) \citep{bair2006prediction, piironen2018} as follows:
\
\begin{equation}
\label{eq:ref_mod}
\begin{aligned}
    Y_{i}|&\boldsymbol{\beta},\sigma^{2},\boldsymbol{u}_{i} \overset{ind}{\sim} N(\boldsymbol{u}_{i}^{T}\boldsymbol{\beta},\sigma^{2}) \quad &i=1,..,n \\
    &\beta_{j}|\!\begin{aligned}[t] &\tau \overset{iid}{\sim} N(0,\tau^{2})\\
    &\tau \sim t_{4}^{+}(0,s_{max}^{-2}) 
    \end{aligned} &j=1,..,5 \\ 
    &\sigma \sim t_{3}^{+}(0,10) \\
\end{aligned}
\end{equation}
where $u_{ij}$ stays for the $j$-th SPC of observation $i$, and $s_{max}$ denotes the sample standard deviation of the largest SPC. We use as screening threshold for the SPCs the value $0.6s_{max}$, which has shown satisfying predictive performance. In our experiments the results are not very sensible to the chosen value, yet a more principled approach would be to use cross-validation to select the threshold as in \cite{paper:projpred}.
\\
The normal means problem formulation is obtained as explained in Section \ref{comparison} by Fisher-transformation. We label as ``ref'' the reference approach, which consists in using the reference model on top of the computation of the z-values, and ``data'' the standard approach based on the observed data only. In Section \ref{shrinkage-signal} we analyse in the context of full-Bayes methods the different shrinkage and signal estimation provided by the use of a reference model or not. Section \ref{complete-selection} shows results for the complete selection procedures.

\hypertarget{shrinkage-signal}{%
\subsubsection{Shrinkage and signal analysis}\label{shrinkage-signal}}
In the framework of full-Bayes methods we analyse the effect of the reference model using two continuous hierarchical shrinkage priors: the Dirichlet-Laplace \citep{paper:dirichlet_laplace} and the regularised horseshoe prior \citep{paper:rhs}. 
% Although the horseshoe+ prior by \cite{bhadra2017horseshoe+} is a state-of-the-art prior for sparse signal analysis in the context of the normal means problem, we decided to include the regularised horseshoe due to its faster MCMC inference, since our purpose in this paper is not to study the best prior choice, but rather compare and show the benefits of using a reference model when carrying out variable selection.
We used an uniform prior on the interval $(1/p,1/2)$ for the Dirichlet hyperparameter of the Dirichlet-Laplace prior, whereas regarding the reguelarised horseshoe prior we followed the indication provided in \cite{paper:rhs}, setting the prior guess of the effective number of parameters equal to 1 to achieve the highest shrinkage. Yet we have not observed any sensibility of the results due to such a choice.
\
Since, as already mentioned, continuous priors do not usually give an automatic selection procedure, in this Section we study the amount of shrinkage and the bias of the posterior median looking at the SESE and the SSE (see definitions \eqref{eq:SSE} and \eqref{eq:SESE}), together with the posterior mean of the shrink factors.

\begin{figure}[tp]
  \centering
  \includegraphics[width=0.98\textwidth]{graphics/post_int.pdf}
  \caption{Posterior intervals for the parameters of the normal means problem ($n=50$, $\rho=0.3$) using the regularised horseshoe prior. Posterior means and one standard deviation intervals depicted. Respectively in red and in blue relevant and non-relevant features. Horizontal dashed line corresponds to the true value of the mean for the relevant features.\\}
  \label{fig:posterior_intervals}
\end{figure}

Figure \ref{fig:posterior_intervals} shows an example of posterior distributions for the model \eqref{eq:normal_means_problem2} using the regularised horseshoe prior. Respectively on the right and on the left the results using or not the reference model approach. It is evident how the reference model helps in tearing apart the signals from the noise, resulting in less biased estimates. This is quantified in Figure \ref{fig:SESE_SSE} where average SESE and SSE are depicted after 100 simulations. We observe that the reference approach (in orange) has a clear lower error estimate for both the SESE and the SSE. As $n$ and $\rho$ grow, the amount of error diminish, as expected, due to a larger amount of information of the relevance of each variable provided by the data. We also note that the two priors seem to achieve very similar results, regardless of the approach used.

\begin{figure}[tp]
  \centering
  \includegraphics[width=0.98\textwidth]{graphics/SESE_SSE.pdf}
  \caption{Average SESE and SSE with one standard deviation error bars after 100 simulations.\\}
  \label{fig:SESE_SSE}
\end{figure}

Figure \ref{fig:k} shows the posterior means for the shrinkage factors of each parameter using the regularised horseshoe prior, averaged after 100 data simulations. Relevant and non-relevant features are respectively highlighted in red and blue. The ideal shrinkage would have $\kappa=0$ when the parameter is a signal, whereas $\kappa=1$ when it is noise. Respectively on the y-axis and on the x-axis are depicted the shrinkage factors using the reference model approach or not. If the reference model did not make any difference, we would expect the points to lie on the diagonal. Non-relevant features happen to lie on average on the diagonal for all the simulated scenario, meaning not evident benefits coming from the reference model. Although when considering the shrinkage amount for the relevant ones, we note that the points always lie under the diagonal, meaning that the reference model is able to shrink less the true signals. Such benefit is proportional to the difficulty of the problem, that is it increases with lower correlation and number of observations. Note that the perfect distinction of the two clusters of features (relevant and non-relevant) observable on both the marginal distributions of the shrinkage factors is due to the averaging over the 100 data simulations. In a single data realisation there would be more noise and the clusters would be closer and overlapping.
The results for the Dirichlet-Laplace prior are very similar and we do not include them in the paper.

\begin{figure}[tp]
  \centering
  \includegraphics[width=0.98\textwidth]{graphics/k_RHS.pdf}
  \caption{Average posterior mean values for the shrinkage factors using the regularised horseshoe prior after 100 simulations. Respectively in red and in blue relevant and non-relevant variables.\\}
  \label{fig:k}
\end{figure}

\hypertarget{complete-selection}{%
\subsubsection{Complete selection analysis}\label{complete-selection}}
As complete selection procedures we consider the control of the local false discovery rate \citep{paper:efron, efron2012large}, the empirical Bayes median \citep{johnstone2004needles} and the selection by posterior credible intervals. 
\\
The control of the local false discovery rate is applied through the \texttt{R}-package \texttt{locfdr}. It consists in testing the z-values $\{z_{j}\}_{j=1}^{p}$ to belong to the theoretical null distribution $f_{0}$ (the null hypothesis, meaning no relevance) against the alternative hypothesis distribution $f_{1}$. In our case $f_{0}$ correspond to the standard normal distribution, see expression \eqref{eq:normal_means_problem2}. The quantity of interest is the local false discovery rate (loc.fdr) defined as:
\
\begin{equation}
loc.fdr(z)=P(H_{0}|z)=\frac{f_{0}(z)\pi_{0}}{f(z)}
\end{equation}
where $\pi_{0}$ is the prior probability of the null hypothesis and $f(z)=\pi_{0}f_{0}(z)+(1-\pi_{0})f_{1}(z)$ is the marginal distribution of the z-values. The latter is estimated using splines with 7 degrees of freedom and we select features with local false discovery rate under the value 0.2. Such a value is commonly suggested only because it corresponds to a Bayes factor large than 36 (assuming $\pi_{0}\geq0.9$), other values can be considered and in our experience do not affect the results of the comparison. We use the default setting to estimate $\pi_{0}$ from the data provided by the package.
\\
The empirical Bayes median procedure is given by the \texttt{R}-package \texttt{EbayesThresh} and consists in fitting a Bayesian model with a prior composed by a mixture of a delta in zero and a heavy-tailed distribution. We use, as suggested, a Laplace distribution resulting in a thresholding property, i.e. there exists a threshold value such that all the data under that threshold have posterior median equal to zero. Therefore the selection is done including those parameters whose posterior median is different from zero. The hyperparameter of the Laplace distribution and the mixing weight of the prior are estimated by marginal maximum likelihood. 
\\
The selection by posterior credible intervals is done using the regularised horseshoe prior and selecting those features whose posterior distribution does not include zero in the interval between the 0.05-th and the 0.95-th quantiles.

Figure \ref{fig:sensitivity_vs_fdr} reports the average sensitivity (on the y-axis) versus the average false discovery rate (x-axis) after 100 data simulations for the different combination of $n$ and $\rho$. For each method (different colours) the square and the circle dots respectively correspond to using or not the reference approach. The best selection performance is on the top-left corner of each plot, meaning lowest false discovery rate and highest sensitivity. It is possible to note that regardless of the method used, the use of a reference model improves the goodness of the selection diminishing the false discovery rate (left shifting) and/or augmenting the sensitivity (up shifting). In accordance with what expected, higher the number of observations and the correlation are, easier the selection is and, thus, the benefits of the reference model are less notable, since the unprocessed data already give enough information to identify the significant variables.

@@

Figure \ref{fig:stability} shows the estimates of the stability measure proposed by \cite{paper:stability} with 0.95 confidence intervals after 100 simulations. Such a measure takes in account the variability of the subset of the selected features at each simulation (originally at each bootstrap sample), modelling the selection of each variable as a Bernoulli process. Further details are available in their paper as asymptotic normal distribution, based on which confidence intervals are computed. The reference model helps improving the stability of the selection: again, such benefit is notable when the problem is more difficult (small $n$ and $\rho$). We observe also less uncertainty in the stability estimates for the reference approach (i.e. the width of the 0.95 confidence intervals), which can be still connected to the overall stability of the procedure.

\begin{figure}[tp]
  \centering
  \includegraphics[width=0.98\textwidth]{graphics/stability.pdf}
  \caption{Stability estimates with 0.95 confidence intervals after 100 data simulations.\\}
  \label{fig:stability}
\end{figure}

\hypertarget{real-world-data}{%
\subsection{Real world data: the body fat dataset}\label{real-world-data}}

>>>>

In our examples, we retrieve the normal means problem from the sample correlations between the target and the covariates using the Fisher $z$-transformation \citep{hawkins1989using}. Suppose we have a continuous target random variable $Y$, a set of $p$ continuous covariates $\{X_{j}\}_{j=1}^{p}$, and let us denote $\rho_{j}=Cor(Y,X_{j})$. Further, suppose we have observed $n$ statistical units and define $r_{j}$ the sample correlation between the observations of the target variables $\{y_{i}\}_{i=1}^{n}$ and the $j$-th covariate $\{x_{ij}\}_{i=1}^{n}$. Finally, we refer to the Fisher $z$-transformation function $\text{tanh}^{-1}(\cdot)$ as $T_{F}(\cdot)$. Assuming each pair $(Y,X_{j})$ to be bivariate normally distributed, the corresponding transformed correlations are approximately normally distributed as well with known variance:
\
\begin{equation} \label{eq:fisher_transformation}
T_{F}(r_{j})\overset{ind}{\sim} N(T_{F}(\rho_{j}),\frac{1}{n-3}) \quad j=1,..,p
\end{equation}
Therefore, rescaling the quantities $T_{F}(r_{j})$ by $\sqrt{n-3}$ and referring to the results as variables $z_{j}$, we again find the formulation \eqref{eq:normal_means_problem} of the normal means problem, this time with unit variance:
\
\begin{equation} \label{eq:normal_means_problem2}
Z_{j}|\theta_{j}\overset{ind}{\sim}N(\theta_{j},1) \quad j=1,..,p
\end{equation}
Note that in thise cse the quantities of interest $\theta_{j}$ are equal to $\sqrt{n-3}\,T_{F}(\rho_{j})$. There are different ways to proceed with the selection in the normal means problem. Here, we consider several state-of-the-art approaches primarily from Bayesian statistics.

We begin by explaining some Bayesian estimation methods to solving the normal means problem. They all have in common that a Bayesian regression model is fitted using some sparsifying prior on the regression coefficients, for example, as discussed in \cite{paper:dirichlet_laplace}, \cite{bhadra2017horseshoe+} and \cite{johnstone2004needles}. If these priors have continuous support, as is the case for the Dirichlet-Laplace (DL; cite) or horseshoe-like priors (cite), there is no canonical way to complete the selection since the posterior probability of an exactly zero signal is always zero. Whereas \cite{paper:dirichlet_laplace} used k-means clustering over the posterior samples to perform the actual selection, \cite{bhadra2017horseshoe+} just focused their analysis on the obtained shrinkage and the correct estimation of the sparse signals without any actual selection. In our experiments, we include the DL prior and the regularised horseshoe (RHS) prior \citep{paper:rhs}, which we think scales better to higher number of covariates as compared to other horseshoe-like priors. For the Bayesian regression models with these priors, we compare the posterior shrinkage and the correct estimation of the sparse signals with and without using a reference model as a noise filter. For this purpose, we consider the   average SSE (sum of square errors) and the average SESE (sum of expected square errors) as quantities measuring estimation accuracy. They are defined as
\
\begin{align}
\text{SSE}&=\frac{1}{n-3}\sum_{j=1}^{p}(\hat{\theta}_{j} - \theta^{0}_{j})^{2} \label{eq:SSE} \\
\text{SESE}&=\frac{1}{n-3}\sum_{j=1}^{p}\int_{\mathbb{R}}(\theta_{j}-\theta^{0}_{j})^{2}p(\theta_{j}|z_{1},..,z_{p})d\theta_{j} \\
&=\frac{1}{n-3}\sum_{j=1}^{p}\mathbb{E}_{\theta_{j}}[(\theta_{j}-\theta^{0}_{j})^{2}|z_{1},..,z_{p}] \label{eq:SESE}
\end{align}
where $\theta_{j}^{0}=\sqrt{n-3}\,T_{F}(\rho_{j})$ is the true value, $\hat{\theta}_{j}$ is the posterior median of each parameter $\theta_{j}$. We divide the errors by $(n-3)$ to have quantities independent of the number of statistical units. Note that the SESE takes the posterior uncertainty in account and thus also the shrinkage of the posterior distributions, whereas the SSE only measures the bias in the point estimates. Note that actually any kind of point estimate could be used to compute the SSE but here we follow \cite{paper:dirichlet_laplace} and use the posterior median. The results that we show later on in Section \ref{shrinkage-signal} are not sensible to such a choice.

For shrinkage priors, one centeral aspect is the amount of shrinkage they actually impose on the relevant and irrelevant features. Ideally, the irrelevant features should be completely shrunken to zero while the relevant features should not be shrunken at all. The amount of shrinkage can be quantitified by the shrinkage factor $\kappa_{j}$ for each parameter $\theta_{j}$ ranging from $0$ (no shrinkage) to $1$ (complete shrinkage). For model \eqref{eq:normal_means_problem2} with a hierarchical shrinkage prior of the type
\begin{align}
Z_{j}|&\theta_{j}\overset{ind}{\sim}N(\theta_{j},1) \qquad j=1,..,p \\
&\theta_{j}|\tau,\nu_{j}\overset{ind}{\sim}N(0,\nu_{j}^{2}\tau^{2})
\end{align}
the shrinkage factor $\kappa_{j}$ is defined as
\begin{equation}
\kappa_{j}=\frac{1}{1+\tau^{2}\nu_{j}^{2}}.
\end{equation}
\
In our case, $\kappa_{j}$ can be computed as
\begin{equation}
\kappa_{j}^{\text{RHS}}=\frac{1}{1+\tau^{2}\lambda_{j}^{2}}, \qquad \kappa_{j}^{\text{DL}}=\frac{1}{1+\psi\phi_{j}^{2}\tau^{2}}
\end{equation}
for the regularised horseshoe and the Dirichlet-Laplace prior respectively. In the left hand-side expression, $\tau$ and $\lambda_{j}$ represent the global and local shrinkage parameters of the regularised horseshoe prior \cite[for further details see][]{paper:rhs}, whereas on the right hand-side, $\psi\phi_{j}^{2}\tau^{2}$ is the variance term of the Dirichlet-Laplace prior of parameter $\theta_{j}$ following the notation of \cite{paper:dirichlet_laplace}. We will use the posterior mean of $\kappa_{j}$ as a point estimate.

Within the set of complete selection procedures, we consider three 
Bayesian methods which are described in the following.
\cite{johnstone2004needles} use a spike-and-slab type prior given by a mixture of a delta distribution in zero and a heavy-tailed distribution \cite[see also][]{paper:spike_slab_mitchell}. When the latter is a Laplace distribution, they show an interesting thresholding property of the median estimator and, based on this observation, present a complete selection procedure using their prior. We refer to this method as EB.med. Further, we use a method to control for the local false discovery rate (loc.fdr) as described in \cite{paper:efron, efron2012large}. Further, we device a simple selection procedure based on posterior credible intervals using the regularised horseshoe prior in which we select covariates whose 90\% credible intervals excludes zero (ci.90). All of these methods provide a complete selection procedure and we compare their performance with and without using a reference model on top of them. As criteria of selection performance, we evaluate the average false discovery rate (i.e., the ratio of the number of non-relevant selected features over the number of selected features) and the average sensitivity (i.e., the ratio of the number of relevant selected features over the total number of relevant features). We also provide a comparison of the stability of the selection by means of a stability measure proposed by \cite{paper:stability}. Table \ref{tab:comparison} summarises the methods used in out numerical experiments.

@@

Here we use simulated data in order to control the difficulty of the selection problem. We rely on the scheme \eqref{eq:simulated_data} using different levels of correlation $\rho\in\{0.3,0.5\}$ and number observation $n\in\{50,70,100\}$. The total number of covariates $p$ and the number of relevant covariates $k$ are fixed to $p = 1000$ and $k = 100$, respectively. In general, the lower $\rho$ and $n$, the more challenging the selection. As mentioned, this data generation mechanism was originally proposed by \cite{paper:projpred} who also devise a reference model performing sufficiently well in this situation. It consists of a linear regression using the first five supervised principal components (SPCs) \citep{bair2006prediction, piironen2018} as covariates and imposing an
hierarchical prior on their coefficients:
\
\begin{equation}
\label{eq:ref_mod}
\begin{aligned}
    Y_{i}|&\boldsymbol{\beta},\sigma^{2},\boldsymbol{u}_{i} \overset{ind}{\sim} N(\boldsymbol{u}_{i}^{T}\boldsymbol{\beta},\sigma^{2}) \quad &i=1,..,n \\
    &\beta_{j}|\!\begin{aligned}[t] &\tau \overset{iid}{\sim} N(0,\tau^{2})\\
    &\tau \sim t_{4}^{+}(0,s_{max}^{-2}) 
    \end{aligned} &j=1,..,5 \\ 
    &\sigma \sim t_{3}^{+}(0,10) \\
\end{aligned}
\end{equation}
In the above, $u_{ij}$ represents the $j$-th SPC evaluated at observation $i$, and $s_{max}$ denotes the sample standard deviation of the largest SPC. As screening threshold for the SPCs, we use the value $0.6s_{max}$, which has shown satisfying predictive performance (TODO: clarify this sentence). In our experiments the results are not very sensible to this choice, yet a more principled approach would be to use cross-validation to select the threshold as done in \cite{paper:projpred}.

The normal means problem formulation is obtained as explained in Section \ref{comparison} by applying the Fisher-z-transformation to the empirical correlations. We label the reference approach as ``ref'', which consists of using the reference model on top of the computation of the z-values, and the standard approach based on the observed data simply as ``data''. In Section \ref{shrinkage-signal}, we analyse the different shrinkage and signal estimates in the context of the full Bayes estimation methods by comparing the ref and data approach. In Section \ref{complete-selection}, we present results for the complete selection procedures.

\hypertarget{shrinkage-signal}{%
\subsubsection{Shrinkage and signal analysis}\label{shrinkage-signal}}
In the framework of fully Bayesian estimation methods, we analyse the effect of the reference model using two continuous hierarchical shrinkage priors: the Dirichlet-Laplace \citep{paper:dirichlet_laplace} and the regularised horseshoe prior \citep{paper:rhs}. 
% Although the horseshoe+ prior by \cite{bhadra2017horseshoe+} is a state-of-the-art prior for sparse signal analysis in the context of the normal means problem, we decided to include the regularised horseshoe due to its faster MCMC inference, since our purpose in this paper is not to study the best prior choice, but rather compare and show the benefits of using a reference model when carrying out variable selection.
For the Dirichlet hyperparameter of the Dirichlet-Laplace prior, we use an uniform prior on the interval $(1/p,1/2)$. For the reguelarised horseshoe prior, we follow the recommendations provided in \cite{paper:rhs} by setting the prior guess of the number of relevant covariates to one in order to achieve the highest possible shrinkage. We have not observed any sensibility of the results due to such a choice.
\
Since, as explained at the start of Section \ref{comparison}, continuous priors usually do not provide an automatic selection procedure, we study the amount of shrinkage and the bias of the posterior medians looking at the SESE and the SSE (see definitions \eqref{eq:SSE} and \eqref{eq:SESE}), together with the posterior mean of the shrinkarge factors.

\begin{figure}[tp]
  \centering
  \includegraphics[width=0.98\textwidth]{graphics/post_int.pdf}
  \caption{Posterior intervals for the parameters of the normal means problem ($n=50$, $\rho=0.3$) using the regularised horseshoe prior. Posterior means and one standard deviation intervals are depicted. Relevant and non-relevant features are displayed in red and in blue respectively. Horizontal dashed lines corresponds to the true value of the mean for the relevant features.\\}
  \label{fig:posterior_intervals}
\end{figure}

Figure \ref{fig:posterior_intervals} shows an example of posterior distributions for the model \eqref{eq:normal_means_problem2} using the regularised horseshoe prior with the data approach on the left and the ref approach on the right-hand side. It is evident how the reference model helps in tearing apart the signal from the noise, resulting in less biased estimates and clearer separation between relevant and irrelevant features. This is quantified in Figure \ref{fig:SESE_SSE} where average SESE and SSE are depicted after 100 simulations. We observe that the reference approach (in orange) has a clearly lower estimate for both the SESE and the SSE. As $n$ and $\rho$ increase, the amount of error diminishes, as expected, due to a larger amount of information of the relevance of each variable provided by the data. We also note that the two priors seem to achieve very similar results under all conditions.

\begin{figure}[tp]
  \centering
  \includegraphics[width=0.98\textwidth]{graphics/SESE_SSE.pdf}
  \caption{Average SESE and SSE with one standard deviation intervals after 100 simulations.\\}
  \label{fig:SESE_SSE}
\end{figure}

Figure \ref{fig:k} shows the posterior means for the shrinkage factors of each parameter using the regularised horseshoe prior, averaged after 100 data simulations. Relevant and non-relevant features are highlighted in red and blue respectively. The ideal shrinkage would be $\kappa=0$ when the parameter is a signal and $\kappa=1$ when it is noise. The shrinkage factors using the data and reference approach are depicted on the y-axis and on the x-axis respectively. If the reference model did not make any difference, we would expect the points to lie on the diagonal. In our simulations, non-relevant features were indeed on the diagonal on average for all the simulated scenarios, which implies that their shrinkage was not improved by the reference approach. However, when considering the amount of shrinkage for the relevant feature, the points are always located under the diagonal, which means that the reference model helped in shrinking true signals less. Such benefit is roughly proportional to the difficulty of the problem, that is it increases with lower correlations and lower number of observations. Note that the perfect distinction of the two clusters of features (relevant and non-relevant) observable on both the marginal distributions of the shrinkage factors is due to the averaging over the 100 data simulations. In a single data realisation, there would be more noise and the clusters would be closer and overlapping. The results for the Dirichlet-Laplace prior are very similar and we do not display them in the paper.

\begin{figure}[tp]
  \centering
  \includegraphics[width=0.98\textwidth]{graphics/k_RHS.pdf}
  \caption{Average posterior mean values for the shrinkage factors using the regularised horseshoe prior after 100 simulations. Relevant and non-relevant variables are displayed in red and blue respectively.\\}
  \label{fig:k}
\end{figure}

\hypertarget{complete-selection}{%
\subsubsection{Complete selection analysis}\label{complete-selection}}
As complete selection procedures we consider the control of the local false discovery rate \citep{paper:efron, efron2012large}, the empirical Bayes median \citep{johnstone2004needles} and the selection by posterior credible intervals. 
\
The control of the local false discovery rate is applied through the \texttt{R}-package \texttt{locfdr}. It consists of testing the z-values $\{z_{j}\}_{j=1}^{p}$ on whether they belong to the theoretical null distribution $f_{0}$ (i.e., the null hypothesis $H_0$ meaning no relevance) against the alternative hypothesis distribution $f_{1}$. In our case $f_{0}$ corresponds to the standard normal distribution (see expression \eqref{eq:normal_means_problem2}). The quantity of interest is the local false discovery rate (loc.fdr) defined as:
\
\begin{equation}
\text{loc.fdr}(z)=P(H_{0}|z)=\frac{f_{0}(z)\pi_{0}}{f(z)}
\end{equation}
where $\pi_{0}$ is the prior probability of $H_0$ and $f(z)=\pi_{0}f_{0}(z)+(1-\pi_{0})f_{1}(z)$ is the marginal distribution of the z-values. The latter is estimated using splines with 7 degrees of freedom. We select features with local false discovery rate below $0.2$. Such a value is commonly suggested only because it corresponds to a Bayes factor larger than 36 (assuming $\pi_{0}\geq0.9$). Other values can be considered and, in our experience, do not affect the results of the comparison. We use the default setting to estimate $\pi_{0}$ from the data provided by the package.
The empirical Bayes median procedure is given by the \texttt{R}-package \texttt{EbayesThresh} and consists of fitting a Bayesian model with a prior composed by a mixture of a delta in zero and a heavy-tailed distribution. As suggested by (cite), we use a Laplace distribution resulting in a thresholding property, that is, there exists a threshold value such that all the data under that threshold have posterior median equal to zero. Therefore the selection is done by selecting only those parameters whose posterior median is different from zero. The hyperparameter of the Laplace distribution and the mixing weight of the prior are estimated by marginal maximum likelihood. 
The selection by 90\% posterior credible intervals is done using the regularised horseshoe prior and selecting those features whose posterior distribution does not include zero in the interval between the 5\% and the 95\% quantiles.

Figure \ref{fig:sensitivity_vs_fdr} reports the average sensitivity on the y-axis) versus the average false discovery rate on the x-axis after 100 data simulations for the different combinations of $n$ and $\rho$. For each method (different colours) the squares and the circles correspond to using the reference and approach respectively. The best selection performance is on the top-left corner of each plot, as it implies the lowest false discovery rate and the highest sensitivity. We see that regardless of the applied selection method, the use of a reference model improves the goodness of the selection as it reduces the false discovery rate (shifting to the left) and/or increasing the sensitivity (shifting upwards). In accordance with what can be expected, the higher number of observations and the higher the true correlations, the easier the selection is. Thus, for easier selection scenarios, the benefits of the reference model are less notable since the unprocessed data already provide enough information to identify the relevant covariates.

@@

Figure \ref{fig:stability} shows the estimates of the stability measure proposed by \cite{paper:stability} with 0.95 confidence intervals after 100 simulations. Such a measure takes in account the variability of the subset of the selected features at each simulation (originally at each bootstrap sample), modelling the selection of each variable as a Bernoulli process. Further details are available in (cite). The reference model helps in improving the stability of the selection: Again, such benefit is more notable when the problem is more difficult (small $n$ and $\rho$). In addition, we observe less uncertainty in the stability estimates for the reference approach (i.e., smaller width of the 0.95 confidence intervals), which can be still connected to the overall stability of the procedure.

\begin{figure}[tp]
  \centering
  \includegraphics[width=0.98\textwidth]{graphics/stability.pdf}
  \caption{Stability estimates with 95\% confidence intervals after 100 data simulations.\\}
  \label{fig:stability}
\end{figure}

\hypertarget{real-world-data}{%
\subsection{The body fat data: A real world example}\label{real-world-data}}
